Untitled

### 2024-10-01 code/manuscript_altanalysis.Rmd
more new analysis

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
```

@@

## Z

@@

@@

>>>>

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
library(ivreg)
library(fixest)
library(sandwich)
library(lmtest)
```

@@

## Z: Competitive Shocks and Y: Outcomes

## Broader definitions 5 / 7 quality measures significant improvements overall
# included.years <- 2009:2021
# included.treat <- 2013:2021

## Original good filters
# included.years <- 2009:2019
# included.treat <- 2013:2019

included.years <- 2010:2023
included.treat <- 2013:2023

df.comp <- uds.covariates %>% 
  select(Year:BHCMISID, Total:Pct.COM) %>% 
  select(BHCMISID, Year, Total:Pct.COM) %>% 
  arrange(BHCMISID, Year) %>% 
  left_join(uds.6a, by = c("BHCMISID","Year" = "YEAR")) %>% 
  left_join(uds.quality.6b %>% select(Year, BHCMISID, imm.rate:adultbmi.denom), by = c("BHCMISID","Year")) %>% 
  left_join(uds.quality.7 %>% 
  filter(Race == " Total" | is.na(Race)) %>% 
  group_by(Year, BHCMISID) %>% 
  summarise(htn.rate = sum(htn.rate * htn.total) / sum(htn.total), 
            htn.total = sum(htn.total), 
            dm.rate = sum(dm.rate * dm.total) / sum(dm.total), 
            dm.total = sum(dm.total)) %>% 
  arrange(BHCMISID, Year), by = c("BHCMISID","Year")) %>% 
    left_join(fins.revenue.expenses, by = c("BHCMISID" = "BHCMIS.ID", "Year" = "form_year")) %>%

  mutate(ID = as.numeric(as.factor(BHCMISID))) %>% 
  arrange(BHCMISID)

df.comp <- df.comp %>% 
  left_join(df.comp %>% 
  group_by(BHCMISID) %>% 
  summarise(counts = n()) %>% filter(counts == length(included.years)), by = c("BHCMISID")) %>% 
  group_by(BHCMISID) %>% 
  mutate(closed = ifelse(is.na(counts) & Year == max(Year), 1, 0)) #%>%  filter(APM %in% c('Yes','No'))

#df.comp$year.rel <- relevel(as.factor(df.comp$year.rel), ref = "-1")

## Filter for balanced panel, remove closures and late openings
df.comp <- df.comp %>%
  left_join(df.comp %>% summarise(Counts = n(), MinYear = min(Year)), by = c("BHCMISID")) #%>%  filter(Counts == length(included.years)) #  filter(Counts < 13 & MinYear == 2009)    filter(Counts == length(included.years))

## Remove some weird shit in CT
df.comp <- df.comp %>% 
  filter(BHCMISID != "01E00010") %>% 
                mutate(HIV.prev = T6A_L1AND2_CB / Total * 100, 
         HIV.care = T6A_L1AND2_CA / T6A_L1AND2_CB,

         HepC.prev = T6A_L4B_CB / Total * 100,
         HepC.care = T6A_L4B_CA / T6A_L4B_CB,

         Asthma.prev = T6A_L5_CB / Total * 100,
         Asthma.care = T6A_L5_CA / T6A_L5_CB,

         # AbnormalPap.prev = T6A_L8_CB / Total * 100,
         # AbnormalPap.care = T6A_L8_CA / T6A_L8_CB,
         #
         # ImmunizationsGiven.prev = T6A_L24_CB / Total * 100,
         # ImmunizationsGiven.care = T6A_L24_CA / T6A_L24_CB,

         HeartDisease.prev = T6A_L10_CB / Total * 100, 
         HeartDisease.care = T6A_L10_CA / T6A_L10_CB,

         # OverweightOrObesity.prev = T6A_L14A_CB / Total * 100, 
         # OverweightOrObesity.care = T6A_L14A_CA / T6A_L14A_CB,

         Depression.prev = T6A_L19A_CB / Total * 100, 
         Depression.care = T6A_L19A_CA / T6A_L19A_CB,

         Diabetes.prev = T6A_L9_CB / Total * 100, 
         Diabetes.care = T6A_L9_CA / T6A_L9_CB,

         Hypertension.prev = T6A_L11_CB / Total * 100, 
         Hypertension.care = T6A_L11_CA / T6A_L11_CB) %>%  #%>%  filter(STATE != 'CT')
select(BHCMISID:Year, Total:Pct.COM, HIV.prev:Hypertension.care , imm.rate:MinYear)

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate + cad.rate + asthma.rate + ivd.rate ) / 9 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)

dfc <- dfc %>% 
  mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = 0.18 * quick_ratio + 0.3 * Profitability + 0.81 * Efficiency + 0.14 * NetWorth) %>% 
  mutate(Att.random = ifelse(Att > 0, Att, NA), 
         Distress = ifelse(Altman < 2.6, 1, 0))

@@

## D: HHI, and Bring them Together

df.zip <- uds.zip %>% 
  inner_join(clinics.in.zips, by = c("ZipCode" = "Zip","ReportingYear" = "Year")) %>% 
  select(BHCMISID, GrantNumber, ReportingYear, ZipCode, NumberofPatients)

df.zip.totals <- df.zip %>% 
  group_by( ReportingYear, ZipCode) %>% 
  summarise(Totals = sum(NumberofPatients))

df.zip <- df.zip %>% 
  left_join(df.zip.totals, by = c("ZipCode","ReportingYear")) %>% 
  group_by(BHCMISID, GrantNumber, ReportingYear) %>% 
  summarise(MS_num = sum(NumberofPatients, na.rm = TRUE), 
            MS_denom = sum(Totals, na.rm = TRUE)) %>% 
  mutate(MS = 100 - (MS_num / MS_denom * 100))

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, log(Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)
```

# Analysis

## Model

df.temptemp <- df.mt %>% 
  rename(ID = ID.x) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman) %>% 
  unique() %>% 
  filter(Year >= 2012)

coeffs <- c(0,0,0,0)

for (k in 1:(ncol(df.temptemp)-13)){

  df.temptemptemp <- df.temptemp
  colnames(df.temptemptemp)[(13+k)] <- "Outcome"
  model <- feols(Outcome ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless  | I(MS/10) ~ value + factor(Year) + factor(ID) , cluster = "ID", data = df.temptemptemp)

  coeffs <- rbind(coeffs, model$coeftable[2,])

}
data.frame(cbind(colnames(df.temptemp)[14:ncol(df.temptemp)], (coeffs[-1,])))

```{r}
df.mt %>% 
  filter(Year >= 2012) %>% 
  mutate(value = ifelse(value > 6, 6, value)) %>% 
  group_by(value) %>% 
  summarise(n(), mean(MS, na.rm = TRUE), mean(Complexity, na.rm = TRUE))
```
